### 2023-03-01 Manuscript/Draft1.Rmd
update manuscript

Fish stocks in this highly productive and economically important region are managed by the National Oceanic and Atmospheric Administration’s (NOAA) Northeast Fisheries Science Center (NEFSC) in Woods Hole, Massachusetts. Federal scientists assess the health and abundance of each commercial fish stock using fishery-independent bottom trawl survey data that has been collected by NOAA throughout the region since 1963 [@azarovitz1981brief; @politis2014northeast]. The survey uses a stratified random design where bottom trawl sampling takes place in predefined strata along the eastern continental shelf. The survey has created a rich time series data set with many uses including species-specific habitat identification, analysis of how environmental conditions influence species abundance, and estimating yearly species abundance trends to help inform stock assessments and ultimately quota limits

The survey takes place twice each year- once in the spring and again in the fall. Since most spatial analyses and  projections of future distributions typically assume a constant survey catchability and/or availability over time, NOAA's survey design includes sampling during approximately the same 2-3 week time period in each season. [[the survey for the entire region takes ~8 weeks to complete each season, the GB strata get covered in a similar time period each season because the survey starts in the south and moves north. But there are times when logistics, e.g., storms, Covid, cause a change in the timing of any particular stratum being sampled. This timing issue has come up in the past and we've looked at it using the dates of sampled stations within a particular stock definition. See for example GBYT_survey_timing_cdf.png taken from the 2018 assessment of Georges Bank yellowtail flounder that I copied into a newly created "miscellaneous" folder on the Google Drive. Given all this, I suggest modifying the wording to something like "NOAA's survey design includes sampling Georges Bank during approximately the same 3-4 week time period in each season"]]

>>>>

Fish stocks in this highly productive and economically important region are managed by the National Oceanic and Atmospheric Administration’s (NOAA) Northeast Fisheries Science Center (NEFSC) in Woods Hole, Massachusetts. Federal scientists assess the health and abundance of each commercial fish stock using fishery-independent bottom trawl survey data that has been collected by NOAA throughout the region since 1963 [@azarovitz1981brief; @politis2014northeast]. The survey uses a stratified random design where bottom trawl sampling takes place in predefined strata along the eastern continental shelf. The survey has created a rich time series data set with many uses including species-specific habitat identification, analysis of how environmental conditions influence species abundance, and estimating yearly species abundance trends to help inform stock assessments and ultimately quota limits. The survey takes place twice each year- once in the spring and again in the fall. Since most spatial analyses and  projections of future distributions typically assume a constant survey catchability and/or availability over time, NOAA's survey design includes sampling Georges Bank during approximately the same 3-4 week time period in each season.
